Interval Probability for Fuzzy Quantum Theories

### 2016-05-08 prob.tex
small comment

>>>>

\amr{
We can use DQC if we have some kind of topology (distances). The idea
will be that we want to prepare state PSI but because of errors etc we
prepare a close state. Well the next closest state will be the next
state in our discrete grid. I am sure that a state that's very close
to PSI can involve some wrapping around.
}
